---
title: "Heifer Raisisng Analysis Report"
subtitle: "Skyview"
author: "UMN Team"
date: "`r Sys.Date()`"
format: 
 pdf:
  geometry:
    - top=25mm
    - bottom=25mm
    - right=25mm
    - left=25mm
  colorlinks: true
  fig-width: 7
  fig-height: 5
  fig-asp: 1
execute:
    echo: false
    message: false
    warning: false
---

```{r load data, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE, paged.print=TRUE}
#Setup and load data change dates and farm in this file
source("01_heifer_import.R")
```

# Introduction

This is an summary of the heifer raising data and performance of purchased and KDD heifers since heifers went to KDD

## Description of animals gone to KDD

@tbl-desc shows descriptive information of the calves that have gone to KDD since `r start_date` .

```{r}
#| label: tbl-desc
#| tbl-cap: "Descriptive info of calves that went to KDD"

source("02_weight_graphs.R")

table_sum
```

\newpage

## Growth of Heifers

@fig-growth shows how calves are growing at KDD according to their breed and the disease status.

<br>

```{r}
#| label: fig-growth
#| fig-cap: "Disease does not seem to impact weights"

graph_wt

```

\newpage

## Growth Rate Table

@tbl-growth show the growth rates for animals that have returned to Skyview according to their breed and disease status.

```{r}
#| label: tbl-growth
#| tbl-cap: "Growth rates for animals that have returned to Skyview"

table_wt

```

\newpage

## Effect of Disease on Age of Return Home

```{r}
#| label: fig-diseae_age
#| fig-cap: "Effect of Disease on age of returning to Skyview"

go_home_age_graph

```

\newpage

## Performance of Purchased vs KDD (Holstein Only)

Comparison of purchased heifers vs KDD heifers is show in @fig-pur.
This for Holsteins only has not a lot of HoJo's are milking yet.
The higher cull rate and the 2-3 lbs difference at 4 and 8 weeks raises the question if that is enough of a difference to pay to raise more heifers at KDD.

<br>

```{r}
#| label: tbl-performane
#| tbl-cap: "Descriptive data on KDD and purchased animals that freshened at Skyview"

source("03_milk_graphs.R")

milk_table
```

\newpage

## Milk Production

@fig-pur compares average daily milk production at week 1, 4 and 8.

```{r}
#| label: fig-pur
#| fig-cap: "KDD heifers make more milk"

milk_graph_half
```

\newpage

## Culling Difference between KDD and purchased animals

Data is presented as survival curves and tables.
Survival curves should be interpreted as longer the line stays close to 100% the better.
Due to small numbers the faded out areas all overlap and indicate the uncertainty around the estimated line.
Survival time is counted as time calving.

```{r}
#| label: fig-cull
#| fig-cap: "KDD heifers last longer"

source("04_culling.R")

km
```

```{r}
#| label: tbl-cull
#| tbl-cap: "Probability of being culled is much higher for purchased heifers"

tbl_surv1

```

\newpage

## Impact of Disease on Milk Production

For animal raised at KDD the following graph and table show impact of disease on productivity

```{r}
#| label: tbl-disease_perfomance
#| tbl-cap: "Disease as calf does not seem to impact performance early in lactation"

disease_sum_table
```

\newpage

### Impact of Disease on Milk Graph

```{r}
#| label: fig-disease_milk
#| fig-cap: "Having a disease as a calf does not impact milk"

milk_disease_graph

```
